The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-13 paper.tex
update

 \Cref{fig__jetI5+ismSeed3-45deg} shows\
 the slices of pressure (top), temperature (middile), number density (bottom)\
 at the end of simulation $t=12.39$ Myr.\
 The slices pass through the bipolar jet source injecting along $z=-y$ direction\
 for a duration $t=0$--$1.2$ Myr.\
 Comparison between the clumpy (first column from left)\
 and the smooth disc (second) in a stratified atmosphere\
 shows that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (third) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
 is always associated with the disc, and without the disc,\
 the outermost bubbles and the turbulent region will be tilted,
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane even the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the inverse shocks are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by an inclined bipolar jets that emanated from the GC 12.39 million years ago,\
      and stretched by stratified ambient subsequently.
\item The nature of the \textit{Fermi} bubbles are essentially a turbulent flows\
      that can stochastically accelerate CRe. Associated with
      contact discontinuity\
\item

\end{itemize}

>>>>

 \Cref{fig__jetI5+ismSeed3-45deg} shows\
 the slices of pressure (top), temperature (middile), number density (bottom)\
 at the end of simulation $t=12.39$ Myr.\
 The slices pass through the bipolar jet source injecting along $z=-y$ direction\
 for a duration $t=0$--$1.2$ Myr.\
 Comparison between the clumpy (first column from left)\
 and the smooth disc (second) in a stratified atmosphere\
 shows that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (third) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
 is always associated with the disc, and without the disc,\
 the outermost bubbles and the turbulent region will be tilted,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

 % shock wave, followed by a contact discontinuity, moves to the right.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane even the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the inverse shocks are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by an inclined bipolar jets that emanated from the GC 12.39 million years ago,\
      and significantly stretched by stratified ambient afterwards.
\item The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed may\
      lead to stochastic acceleration of CRe, and balanced with radiative cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\end{itemize}
